ML parameters

### 2023-01-30 workflow/notebooks/ml-params.Rmd
Switch to intersection dataset for otu comp

## taxlevel - OTU vs genus
```{r plot_taxlevel}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('taxlevel')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, taxlevel, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(x="performance on held out test data")

>>>>

## taxlevel - OTU vs genus
```{r plot_taxlevel}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'int', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('taxlevel')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'int', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, taxlevel, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name') +
  labs(x="performance on held out test data")
